\begin{thebibliography}{9}

\bibitem{dyrrdal_grid}
Dyrrdal V. Anita, Skaugen Thomas, Stordal Frode, Førland J. Eirik \\
\textit{Estimating areal precipitation in Norway from a gridded dataset}\\
\url{https://doi.org/10.1080/02626667.2014.947289} \\
Hydrological Science Journal, 2015.\\

\bibitem{dyrrdal_bay}
Dyrrdal V. Anita, Lenkoski Alex, Thorarinsdottir L. Thordis, Stordal Frode
\textit{Bayesian hierarchical modeling of extreme hourly precipitation in Norway}
Published: 2014

\bibitem{lapsrate}
@article{article,
author = {Mokhov, I. and Akperov, Mirseid},
year = {2006},
month = {07},
pages = {430-438},
title = {Tropospheric lapse rate and its relation to surface temperature from reanalysis data},
volume = {42},
journal = {Izvestiya, Atmospheric and Oceanic Physics},
doi = {10.1134/S0001433806040037}
}

\bibitem{lutz_idf}
Lutz Julia, Grinde Lars, Dyrrdal V. Anita
\textit{Estimating Rainfall Design Values for the City of Oslo, Norway - Comparison of Methods and Quantification of Uncertainty}
Published: 2020

\bibitem{seity_arome}
Seity Y, Brousseau P, Malardel S, Hello G, Bénard P, Bouttier F,
Lac C, Masson V (2011) The AROME-France convective-scale
operational model. Mon Weather Rev 139(3):976–991. https ://doi.
org/10.1175/2010M WR342 5.1

\bibitem{rogers}
Rogers R.R, Yau M.K (1996). A Short Course in Cloud Physics. Third Edition.International Series in Natural Philosophy.
Butterworth-Heinemann, Elsevier.
ISBN 0-7506-3215-1 

\bibitem{lind_arome}
Lind P, Belušić D, Christensen B. O., Dobler A, Kjellström E, Landgren O, Lindstedt D, Matte D, Perdersen A. R, Toivonen E, Wang F
\textit{Benefits and added value og convetion-permitting climate modeling over Fenno-Scandinavia}
Published 2020

\bibitem{erai}
Berrisford P, Dee D, Poli P, Brugge R, Fielding K, Fuentes M, Kållberg P, Kobayashi S, Uppala S, Simmons A (2011)
The ERA-Interim archive Version 2.0. ERA Report. ECMWF. Shinfield Park, Reading. URL: https://www.ecmwf.int/node/8174

\bibitem{bengtsson_arome}
Bengtsson L, Andrae U, Aspelien T, Batrak Y et al (2017) The HARMONIE–
AROME model configuration in the ALADIN–HIRLAM
NWP system. Mon Weather Rev 145:1919–1935. https ://
doi.org/10.1175/MWR-D-16-0417.1

\bibitem{belusic_hclim}
Belušić, D., de Vries, H., Dobler, A., Landgren, O., Lind, P., Lindstedt, D., Pedersen, R. A., Sánchez-Perrino, J. C., Toivonen, E., van Ulft, B., Wang, F., Andrae, U., Batrak, Y., Kjellström, E., Lenderink, G., Nikulin, G., Pietikäinen, J.-P., Rodríguez-Camino, E., Samuelsson, P., van Meijgaard, E., and Wu, M.: HCLIM38: a flexible regional climate model applicable for different climate zones from coarse to convection-permitting scales, Geosci. Model Dev., 13, 1311–1333, https://doi.org/10.5194/gmd-13-1311-2020, 2020.

\bibitem{lindstedt_hclim}
Lindstedt D, Lind P, Kjellström E, Jones C (2015) A new regional
climate model operating at the meso-gamma scale: performance
over Europe. Tellus A Dyn Meteorol Oceanogr 67:1. https ://doi.
org/10.3402/tellu sa.v67.24138

\bibitem{lind_hclim}
Lind P, Lindstedt D, Kjellström E, Jones C (2016) Spatial and temporal
characteristics of summer precipitation over central Europe in a
suite of high-resolution climate models. J Clim 29:3501–3518.
https ://doi.org/10.1175/JCLI-D-15-0463.1

\bibitem{gmao}
URL: \url{kilde https://gmao.gsfc.nasa.gov/research/subseasonal/atlas/GEV-RV-html/GEV-RV-description.html}

\bibitem{labus}
Labus, M., Labus, K. Thermal conductivity and diffusivity of fine-grained sedimentary rocks. J Therm Anal Calorim 132, 1669–1676 (2018). \\
URL: \url{https://doi.org/10.1007/s10973-018-7090-5}

\bibitem{muller}
MÜller et al. 2017\\
\textit{AROME-MetCoOp: A Nordic Convective-Scale Operational
Weather Prediction Model}\\
URL: \url{https://doi.org/10.1175/WAF-D-16-0099.1}

\bibitem{metreport}
URL: \url{file:///C:/Users/Eirik%20N/Downloads/Met_info_27_2019_styrtregn_B%C3%A6rum_20190807_v02%20(3).pdf}

\bibitem{finse}
Webpage of Finse Alpine Research Ceenter\\
URL: \url{https://www.finse.uio.no/about/location/}\\
Visited 20th of April 2020

\bibitem{seklima}
Historical precipitation records from Finse.\\
URL: \url{https://seklima.met.no/observations/}

\bibitem{yr}
Webpage of Nowegian forcasting service YR for historical data for Finse.\\
URL: \url{https://www.yr.no/nb/historikk/graf/1-111123/Norge/Vestland/Ulvik/Finse}

\bibitem{hosk}
Hosking, J.R.; Wallis, J.R. Parameter and quantile estimation for the generalized Pareto distribution.
Technometrics 1987, 29, 339–349.
https://www.tandfonline.com/doi/pdf/10.1080/00401706.1987.10488243?needAccess=true

\bibitem{olsson}
Olsson, J.; Södling, J.; Berg, P.;Wern, L.; Eronn, A. Short-duration rainfall extremes in Sweden: A regional
analysis. Hydrol. Res. 2019, 50, 945–960.
https://iwaponline.com/hr/article/50/3/945/65595/Short-duration-rainfall-extremes-in-Sweden-a

\bibitem{huard}
Huard, D.; Mailhot, A.; Duchesne, S. Bayesian estimation of intensity–duration–frequency curves and of
the return period associated to a given rainfall event. Stoch. Environ. Res. Risk Assess. 2010, 24, 337–347.
https://link.springer.com/article/10.1007%2Fs00477-009-0323-1

\bibitem{mohymont}
B. Mohymont, G. R. Demarée, D. N. Faka. Establishment of IDF-curves for precipitation in the
tropical area of Central Africa - comparison of techniques and results. Natural Hazards and Earth
System Science, Copernicus Publications on behalf of the European Geosciences Union, 2004, 4 (3),
pp.375-387. ffhal-00299129f
https://hal.archives-ouvertes.fr/hal-00299129/document

\bibitem{fevd}
URL: https://www.rdocumentation.org/packages/extRemes/versions/2.0-12/topics/fevd
RDocumentation of function: fevd : from the extRemes package in R.

\bibitem{nhat}
(Nhat et al., 2006)
Establishment of Intensity-Duration-Frequency Curves
for Precipitation in the Monsoon Area of Vietnam
Found in local forlder IDF

\bibitem{R}
R Core Team (2013). R: A language and environment for statistical
computing. R Foundation for Statistical Computing, Vienna, Austria.
URL http://www.R-project.org/.

\bibitem{Rextremes}
https://cran.r-project.org/web/packages/extRemes/extRemes.pdf


\end{thebibliography} 